The trend in asymmetric drift across the blue cloud

### 2017-12-13 ms.tex
test
reference edits

@@

Asymmetric drift (AD) is the lag of the mean rotation velocity of the
stellar disk behind the circular speed defined by the total
gravitational potential.  Although it is often considered a nuisance
correction one must apply in circular-speed calculations, the direct
connection between AD and the stellar phase-space distribution function
makes it an interesting dynamical properties of galaxies in and of
itself.  The SDSS-IV/MaNGA survey provides more than an order of
magnitude increase in any galaxy sample size useful for AD measurements.
In this pilot Letter, we study the empirical correlation between AD, or
more precisely the differential tangential lag between the stellar
component and \halpha-emitting gas, and global photometric properties
from the NASA-Sloan Atlas.  We isolate a set of galaxies with \halpha\
and stellar velocity fields that are well-fit by simple disk models.
Our sample of $\sim$800 galaxies shows a clear correlation between
absolute $i$-band magnitude and AD measured at half an effective radius.
Removing the primary dependence on the rotation speed, we find that the
stellar disk rotation is 90\% of the \halpha\ rotation speed, in the
mean.  Our sample size allows us to infer a weak, yet statistically
significant, trend with galaxy $N-r$ color such that, in the mean,
redder galaxies have moderately larger AD relative to their rotation
speeds.  Within the context of an albeit strong set of assumptions,
including a direct proportionality between AD and stellar velocity
dispersion as seen in the Milky Way, we argue that our results suggest
little variation in the mean disk mass-to-light ratio as a function of
absolute magnitude and only modest variations with galaxy color
\comment{last sentence TBD; is Figure 3 consistent with SPS
variations?}.

@@

For ensembles of stars in a galaxy disk, \citet[][Section
4.4.3]{2008gady.book.....B} provide an intuitive description of
asymmetric drift (AD) as arising due to the combined effect of the
radially decreasing surface-density and velocity-dispersion profiles
typical of axisymmetric systems.  Using the $v_R$ moment of the
collisionless Boltzmann equation, one obtains the Jeans \comment{ref}
equation that directly relates the circular speed ($v_c$), the mean
stellar tangential speed ($\overline{v_\theta}$), and the stellar
velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term --- describing the
covariance between the radial and vertical motions as a function of
perpendicular distance to the plane of symmetry --- is negligible
\comment{cf.  Cuddeford \& Amendt}.

Asymmetric drift has been measured in numerous systems.  Perhaps most
notably, e.g., \comment{Dehnen \& Binney} have shown that populations of
stars show a direct correlation between their velocity dispersion and
the degree to which their mean rotation speed lags behind that of the
Local Standard of Rest (LSR), much in line with the expectation provided
by equation \ref{eq:adformal}.  Although there have been some studies of
AD in external galaxies \comment{refs}, it is often treated as a
nuisance phenomenon that must be corrected for when trying to constrain
the circular speed curve of a galaxy \comment{refs}.  The ubiquity and
phenomenology of AD as a salient observable has not yet been studied for
a statistically significant population of galaxies.  Our aim is
therefore to provide a first look at the correlation between AD
measurements and basic broad-band photometric properties for a large
sample of galaxies.

@@

In addition to the basic understanding of this dynamically relevant
quantity, our interest in AD stems from its fundamental dynamical
connection to the full phase-space distribution function of a galaxy's
stars, as empirically demonstrated in the Milky Way.  Indeed,
\comment{Westfall et al. (2011; see also refs} used AD to constrain the
axial ratios of the SVE given direct measurements of the line-of-sight
(LOS) stellar velocity dispersion, $\sigma$.  Alternatively, if one can
statistically constrain the shape of the SVE \comment{refs},
measurements of AD could be used as a proxy for stellar $\sigma$ by
either appealing to equation \ref{eq:adformal} or an empirical relation
calibrated by samples with both AD and $\sigma$ measurements \comment{in
prep...}.  Such a use of AD as a proxy for stellar $\sigma$ is
attractive in the low-surface-brightness and low-velocity-dispersion
regimes where direct measurements are difficult and/or expensive.  We
commit to this paradigm by using the following nomenclature for AD,
following from equation \ref{eq:adformal}:
%
\begin{equation}
%
\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2.
%
\label{eq:addef}
%
\end{equation}

@@

We present the data used for our analysis in the following section.  In
Section \ref{sec:results}, we demonstrate that there is a strong
correlation between the absolute $i$-band magnitude of a galaxies and
the strength of its AD measured at half of an effective radius (0.5
$R_{\rm eff}$).  We also illustrate the weak color dependence in this
relation.  We summarize and discuss these results in Section
\ref{sec:discussion}. \comment{flesh out}

@@

We use integral-field spectroscopy from the SDSS-IV/MaNGA (Mapping
Nearby Galaxies from APO) Survey to construct stellar and ionized-gas
velocity fields for 2715 unique galaxies, 39 of which have multiple
observations.  The kinematic measurements are provided by the MaNGA data
analysis pipeline \comment{DAP; Westfall et al., in prep}: the
ionized-gas kinematics are based on simple single-Gaussian fits to the
\halpha\ emission feature and the stellar kinematics are determined
using {\tt pPXF} (Cappellari et al.) with the MILES stellar template
library \comment{Jesus FB et al.}.

The MaNGA galaxy selection \comment{Wake et al} is a simple cut in
absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
complete \comment{check} sampling of the overall galaxy population.  As
such, measurements of stellar and/or \halpha\ rotation curves for some
systems will be difficult/impossible.  Using the photometry from the
NASA-Sloan Atlas \comment{ref},\footnote{\url{nsatlas.org}} Figure
\ref{fig:sample} shows the color-magnitude diagram of all galaxies
colored by their mean \halpha\ and $r$-band surface brightness.
\comment{ Check the details of how this plot was constructed}  Although
not excluded from our velocity-field analysis {\em a priori}, we expect
to obtain poor rotation-curve measurements for galaxies with low
\halpha\ and stellar surface brightness.\footnote{
%
The uniformity of the MaNGA survey \comment{Law et al. 2015} is such
that the signal-to-noise (S/N) of the datacube spaxels is tightly
correlated with surface brightness.}

@@

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by \comment{Andersen \& Bershady (2013)};
see also \comment{Westfall et al. (2011)}.  In three independent fitting
iterations, the model fits are optimized for the \halpha\ velocity
field, the stellar velocity field, and simultaneously for both data
sets; for the latter, the geometry is forced to be the same for the two
dynamical tracers, but the parametrized rotation curves are independent.
We use these velocity-field-fitting results to objectively isolate a set
of ``kinematically regular'' galaxies.  Briefly, galaxies in this sample
must have: (i) successful velocity-field fits for all three approaches,
(ii) differences in the measured \halpha\ and stellar systemic velocity
of less than 20 km/s, (iii) dynamical centers that are consistent to
within a fiber diameter of the morphological center \comment{check the
details of this}, (iv) \halpha\ and stellar velocity-field position
angles that are consistent to within $\pm$15$\arcdeg$, and (v) kinematic
inclinations between $15\arcdeg < i < 80\arcdeg$ that are both
consistent between the \halpha\ and stellar data and with respect to the
photometric ellipticity to within $\pm$20$\arcdeg$.  The constraint on
the inclination is by far the most stringent. \comment{give number of
galaxies cut by each criterion?}  Applying these constraints yields a
sample of 798 observations (for 790 unique galaxies) out of the 2764
observations analyzed.  Eleven galaxies with repeat observations satisfy
the selection criteria; however, only five of these show all
observations are consistently selected, whereas the other six show one
or more of the observations did not pass our constraints \comment{we
should understand why repeat observations are not consistent for the
majority of cases.  low S/N?}.  \comment{Do this or remove the
sentence:} Finally, we also visually inspected the broad-band imaging of
these 790 galaxies and eliminated merging and highly extincted (highly
inclined) systems yielding a final sample of XXX galaxies.  We hereafter
refer to galaxies that satisfy our selection criteria as the ``AD
sample''.

@@

\comment{Show histogram of kinematically regular sample against the
volume-corrected distribution of the MaNGA parent sample in Mi and N-r,
and discuss.}

@@

We plot $M_i$ versus $v_{{\rm H}\alpha}$, $\sigma_a^2$, and
$\sigma_a/v_{{\rm H}\alpha}$ in Figures \ref{fig:correlation}(b),
\ref{fig:correlation}(c), and \ref{fig:correlation}(d), respectively.
The points are colored according to the label to the right of each color
bar.  Each panel provides the Spearman rank-correlation coefficient,
$r_s$, of the plotted data with errors derived from $10^3$ bootstrap
simulations.  We have also used a Markov Chain Monte Carlo
\comment{refs} to sample the Bayesian posterior distribution for a
linear regression to the data in each panel, incorporating the errors in
both axes \comment{refs}; the errors in the kinematic quantities always
dominate over the absolute magnitude errors.  The fitted model is a line
in parametric form with an intrinsic Gaussian scatter perpendicular to
the line.  That is, the line is defined as $\mathbf{l}(t) = \mathbf{l}_0
+ t\ \hat{\mathbf{l}}$ for a generalized coordinate $t$ along the line,
an origin $\mathbf{l}_0 = \{x_0, y_0\}$, and the unit vector
$\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The fitted parameters are
$y_0$, $\phi$, and the dispersion of the intrinsic Gaussian scatter
about the line, $\varepsilon$; $x_0$ is fixed at the median abscissa of
the data being fitted ($x_0 = M_{i,0} = -20.6$).  Uniform priors are
used for $y_0$ and $\phi$ and a logarithmic prior \comment{check this is
true} is used for $\varepsilon$ \comment{ref}.  Using the returned
samples of the posterior, we also provide parameters for the
slope-intercept form of the line --- $y = mx + b$ where $m = \tan\phi$
and $b = y_0 - x_0 \tan\phi$ --- and the scatter projected along the
ordinate, $\varepsilon_y = \varepsilon/|\cos\phi$|.  Table
\ref{tab:lines} provides the median and standard deviation of the
marginalized distribution of each parameter; these parameters have been
used to construct the lines provided in Figure \ref{fig:correlation}.

@@

As expected, there is a strong correlation between $v_{{\rm H}\alpha}$
and $M_i$.  However, it is important to note that Figure
\ref{fig:correlation}(b) does not present the Tully-Fisher \comment{ref}
relation for our AD sample; the Figure gives the rotation speed at
$R=0.5R_{\rm eff}$, not a measure of the full-width of the dynamically
broadened line profile.  The slope of the relation in Figure
\ref{fig:correlation}(b) is steeper than a nominal Tully-Fisher relation
because galaxies at low luminosity tend to have more slowly rising
rotation curves \comment{refs}, which can be confirmed by plotting
$h_{v,{\rm H}\alpha}/R_{\rm eff}$ as a function of $M_i$.
\comment{actually show this?}

@@

If $\sigma_a$ or $v_{{\rm H}\alpha}$ was a secondary parameter in the
distribution of $(M_i,v_{{\rm H}\alpha})$ or $(M_i,\sigma_a^2)$,
respectively, we should expect a gradient in the point color in Figures
\ref{fig:correlation}(b) and \ref{fig:correlation}(c) {\em
perpendicular} to the fitted regression.  However, we see that the
primary gradient in point color is parallel to the fitted regression.
This is consistent with the result that there is little to no
correlation between $M_i$ and $\sigma_a/v_{{\rm H}\alpha}$, as shown in
Figure \ref{fig:correlation}(d):  Both $r_s$ and $\phi$ are small and
only marginally significant with respect to their errors.  From equation
\ref{eq:dproj}, this implies that the deprojected stellar rotation is a
roughly constant fraction of the ionized-gas rotation speed, with
$v_{\ast} \sim 0.9 v_{{\rm H}\alpha}$.  Although the radius at which the
AD was sampled is different, this ratio is consistent with a similar
ratio measured for DiskMass-Survey galaxies \comment{Martinsson et al.}.

The points in Figure \ref{fig:correlation}(d) are colored by the global
$N-r$ color; however, it is difficult to determine from this
illustration if their is any correlation between $\sigma_a/v_{{\rm
H}\alpha}$ and global galaxy color.  One might expect such a correlation
if, for example, galaxies with different global color have different
light-weightings of the thin vs. thick-disk \comment{refs; not sure
there are relevant ones; Comer\'{o}n?}, which propagates to a difference
in which component dominates the dynamical pressure in the disk
midplane.  Figure \ref{fig:colortrend} assesses this directly by
plotting the error-weighted mean trend in $\sigma_a/v_{{\rm H}\alpha}$
for quartiles of the $N-r$ distribution of the AD sample.  The error
bars represent the error-weighted standard deviation of the data in each
bin, whereas the error-weighted standard error is always {\it smaller
than the plotted point}.  This suggests a marginal, yet statistically
significant, detection of a slightly larger $\sigma_a/v_{{\rm H}\alpha}$
in the reddest bin.

>>>>

% Project collaborators: Matthew Bershady, Anne-Marie Weijmans, Karen
% Masters, Michael Merrifield, Jo Bovy, Kevin Bundy, Niv Drory, Thomas
% Martinsson, Joel Brownstein, Daniel Thomas, Dmitry Bizyaev, David Law,
% Andres Meza, Aaron A. Dutton

@@

Asymmetric drift (AD) is the lag of the mean rotation velocity of the
stellar disk behind the circular speed defined by the total
gravitational potential.  Although it is often considered a nuisance
correction one must apply in circular-speed calculations, the direct
connection between AD and the stellar phase-space distribution function
makes it an interesting dynamical properties of galaxies in and of
itself.  The SDSS-IV/MaNGA survey provides more than an order of
magnitude increase in any galaxy sample size useful for AD measurements.
In this pilot study, we demonstrate the empirical correlation between
AD, or more precisely the differential tangential lag between the
stellar component and \halpha-emitting gas, and global photometric
properties from the NASA-Sloan Atlas.  We isolate a set of galaxies with
\halpha\ and stellar velocity fields that are well-fit by simple disk
models.  Our sample of $\sim$800 galaxies shows a clear correlation
between absolute $i$-band magnitude and AD measured at half an effective
radius.  Removing the primary dependence on the rotation speed, we find
that the stellar disk rotation is 90\% of the \halpha\ rotation speed,
in the mean.  Our sample size allows us to infer a weak, yet
statistically significant, trend with galaxy $N-r$ color such that, in
the mean, redder galaxies have moderately larger AD relative to their
rotation speeds.  Within the context of an albeit strong set of
assumptions, including a direct proportionality between AD and stellar
velocity dispersion as seen in the Milky Way, we argue that our results
suggest little variation in the mean disk mass-to-light ratio as a
function of absolute magnitude and only modest variations with galaxy
color \comment{last sentence TBD; is Figure 3 consistent with SPS
variations?}.

@@

For ensembles of stars in a galaxy disk, \citet[][Section
4.4.3]{2008gady.book.....B} provide an intuitive description of
asymmetric drift (AD) as arising due to the combined effect of the
radially decreasing surface-density and velocity-dispersion profiles
typical of axisymmetric systems.  Using the $v_R$ moment of the
collisionless Boltzmann equation, one obtains the Jeans equation
\citep{Jeans1919} that directly relates the circular speed ($v_c$), the
mean stellar tangential speed ($\overline{v_\theta}$), and the stellar
velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term --- describing the
covariance between the radial and vertical motions as a function of
perpendicular distance to the plane of symmetry --- is negligible
\citep{1991ApJ...368...79A}.

Asymmetric drift has been measured in numerous systems.  Perhaps most
notably, e.g., \comment{Dehnen \& Binney} have shown that populations of
stars show a direct correlation between their velocity dispersion and
the degree to which their mean rotation speed lags behind that of the
Local Standard of Rest (LSR), much in line with the expectation provided
by equation \ref{eq:adformal}.  Although there have been some studies of
AD in external galaxies \comment{refs}, it is often treated as a
nuisance phenomenon that must be corrected for when trying to constrain
the circular speed of a galaxy \comment{refs}.  The ubiquity and
phenomenology of AD as a salient observable has not yet been studied for
a statistically significant population of galaxies.  Our aim is
therefore to provide a first look at the correlation between AD
measurements and basic broad-band photometric properties for a large
sample of galaxies.

@@

In addition to the basic understanding of this dynamically relevant
quantity, our interest in AD stems from its fundamental dynamical
connection to the full phase-space distribution function of a galaxy's
stars, as empirically demonstrated in the Milky Way.  Indeed,
\citet{2011ApJ...742...18W} used AD to constrain the axial ratios of the
SVE given direct measurements of the line-of-sight (LOS) stellar
velocity dispersion, $\sigma$.  Alternatively, if one can leverage
statistical constraints on the shape of the SVE
\citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can be used as a
proxy for stellar $\sigma$ via equation \ref{eq:adformal}.  Such a use
of AD-$\sigma$ relation is attractive in the low-surface-brightness and
low-velocity-dispersion regimes where direct measurements are difficult
and/or expensive.  We commit to this paradigm by using the following
nomenclature for AD, following from equation \ref{eq:adformal}:
%
\begin{equation}
%
\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2.
%
\label{eq:addef}
%
\end{equation}

@@

We present the data used for our analysis in the following section.
Section \ref{sec:results} presents the strong correlation seen in out
galaxy sample between the absolute $i$-band magnitude and AD signal
measured at half of an effective radius (0.5 $R_{\rm eff}$).  We also
illustrate the weak color dependence in this relation.  Finally, we
summarize and discuss these results in Section \ref{sec:discussion}.
\comment{flesh out}

@@

We use integral-field spectroscopy from the SDSS-IV/MaNGA (Mapping
Nearby Galaxies from APO) Survey to construct stellar and ionized-gas
velocity fields for 2715 unique galaxies, 39 of which have multiple
observations.  The kinematic measurements are provided by the MaNGA data
analysis pipeline \comment{DAP; Westfall et al., in prep}: the
ionized-gas kinematics are based on simple single-Gaussian fits to the
\halpha\ emission feature and the stellar kinematics are determined
using {\tt pPXF} (Cappellari et al.) with the MILES stellar template
library \comment{Jesus FB et al.}.  \comment{Mention hierarchical
clustering?}

The MaNGA galaxy selection \citep{2017AJ....154...86W} is a simple cut
in absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
complete sampling of the overall galaxy population.  As such,
measurements of stellar and/or \halpha\ rotation curves for some systems
will be difficult/impossible.  Using the photometry from the NASA-Sloan
Atlas,\footnote{\url{nsatlas.org}} Figure \ref{fig:sample} shows the
color-magnitude diagram of all galaxies colored by their mean \halpha\
and $r$-band surface brightness.  \comment{Update this} Although not
excluded from our velocity-field analysis {\em a priori}, we expect to
obtain poor rotation-curve measurements for galaxies with low \halpha\
and stellar surface brightness.\footnote{
%
The uniformity of the MaNGA survey \citet{2015AJ....150...19L} is such
that the signal-to-noise (S/N) of the datacube spaxels is tightly
correlated with surface brightness.}

@@

\comment{Primary vs. Secondary sample?}

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by \citep[][see also
\citealt{2011ApJ...742...18W}]{2003ApJ...599L..79A}.  In three
independent fitting iterations, the model fits are optimized for the
\halpha\ velocity field, the stellar velocity field, and simultaneously
for both data sets; for the latter, the geometry is forced to be the
same for the two dynamical tracers, but the parametrized rotation curves
are independent.  We use these velocity-field-fitting results to
objectively isolate a set of ``kinematically regular'' galaxies.
Briefly, galaxies in this sample must have: (i) successful
velocity-field fits for all three approaches, (ii) differences in the
measured \halpha\ and stellar systemic velocity of less than 20 km/s,
(iii) dynamical centers that are consistent to within a fiber diameter
of the morphological center \comment{check the details of this}, (iv)
\halpha\ and stellar velocity-field position angles that are consistent
to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
\halpha\ and stellar data and with respect to the photometric
ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
inclination is by far the most stringent. \comment{give number of
galaxies cut by each criterion?}  Applying these constraints yields a
sample of 798 observations (for 790 unique galaxies) out of the 2764
observations analyzed.  Eleven galaxies with repeat observations satisfy
the selection criteria; however, only five of these show all
observations are consistently selected.  The remaining six show one or
more of the observations did not pass our constraints \comment{we should
understand why repeat observations are not consistent for the majority
of cases.  low S/N?}.  \comment{Do this or remove the sentence:}
Finally, we also visually inspected the broad-band imaging of these 790
galaxies and eliminated merging and highly extincted (highly inclined)
systems yielding a final sample of XXX galaxies.  We hereafter refer to
galaxies that satisfy our selection criteria as the ``AD sample''.

\comment{limitations of an infinitely thin disk fit?}

@@

\comment{Show histogram of kinematically regular sample against the
volume-corrected distribution of the MaNGA parent sample in Mi and N-r,
and discuss?}

@@

We plot $M_i$ versus $v_{{\rm H}\alpha}$, $\sigma_a^2$, and
$\sigma_a/v_{{\rm H}\alpha}$ in Figures \ref{fig:correlation}(b),
\ref{fig:correlation}(c), and \ref{fig:correlation}(d), respectively.
The points are colored according to the label to the right of each color
bar.  Each panel provides the Spearman rank-correlation coefficient,
$r_s$, of the plotted data with errors derived from $10^3$ bootstrap
simulations.  We have also used a Markov Chain Monte Carlo to sample the
Bayesian posterior distribution for a linear regression to the data in
each panel, incorporating the errors in both axes \citep[see,
e.g.][]{2010arXiv1008.4686H}; the errors in the kinematic quantities
always dominate over the absolute magnitude errors.  The fitted model is
a line in parametric form with an intrinsic Gaussian scatter
perpendicular to the line.  That is, the line is defined as
$\mathbf{l}(t) = \mathbf{l}_0 + t\ \hat{\mathbf{l}}$ for a generalized
coordinate $t$ along the line, an origin $\mathbf{l}_0 = \{x_0, y_0\}$,
and the unit vector $\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The
fitted parameters are $y_0$, $\phi$, and the dispersion of the intrinsic
Gaussian scatter about the line, $\varepsilon$; $x_0$ is fixed at the
median abscissa of the data being fitted ($M_{i,0} = -20.6$).  Uniform
priors are used for $y_0$ and $\phi$ and a logarithmic prior
\comment{check this is true} is used for $\varepsilon$
\citep{MacKay:itp}.  Using the returned samples of the posterior, we
also provide parameters for the slope-intercept form of the line --- $y
= mx + b$ where $m = \tan\phi$ and $b = y_0 - x_0 \tan\phi$ --- and the
scatter projected along the ordinate, $\varepsilon_y =
\varepsilon/|\cos\phi$|.  Table \ref{tab:lines} provides the median and
standard deviation of the marginalized distribution of each parameter;
these parameters have been used to construct the lines provided in
Figure \ref{fig:correlation}.

\comment{Show the PDFs?}

@@

As expected, there is a strong correlation between $v_{{\rm H}\alpha}$
and $M_i$.  However, it is important to note that Figure
\ref{fig:correlation}(b) does not present the
\citet{1977A&A....54..661T} relation for our AD sample; the Figure gives
the rotation speed at $R=0.5R_{\rm eff}$, not a measure of the
full-width of the dynamically broadened line profile.  The slope of the
relation in Figure \ref{fig:correlation}(b) is steeper than a nominal
Tully-Fisher relation because galaxies at low luminosity tend to have
more slowly rising rotation curves \comment{refs}, which can be
confirmed by plotting $h_{v,{\rm H}\alpha}/R_{\rm eff}$ as a function of
$M_i$.  \comment{actually show this?}

@@

If $\sigma_a$ or $v_{{\rm H}\alpha}$ was a fully orthogonal secondary
parameter in the distribution of $(M_i,v_{{\rm H}\alpha})$ or
$(M_i,\sigma_a^2)$, respectively, we should expect a gradient in the
point color in Figures \ref{fig:correlation}(b) and
\ref{fig:correlation}(c) {\em perpendicular} to the fitted regression.
However, we see that the primary gradient in point color is parallel to
the fitted regression.  This is consistent with the result that there is
little to no correlation between $M_i$ and $\sigma_a/v_{{\rm H}\alpha}$,
as shown in Figure \ref{fig:correlation}(d):  Both $r_s$ and $\phi$ are
small and only marginally significant with respect to their errors.
From equation \ref{eq:dproj}, this implies that the deprojected stellar
rotation is roughly a constant fraction of the ionized-gas rotation
speed, with $v_{\ast} \sim 0.9 v_{{\rm H}\alpha}$ \comment{give
scatter}.  Although the radius at which the AD was sampled is different,
this ratio is consistent with a similar ratio measured for
DiskMass-Survey galaxies \citep{2013A&A...557A.130M}.

\comment{Need to revisit this paragraph in the context of the
bulge-to-disk fraction.}  The points in Figure \ref{fig:correlation}(d)
are colored by the global $N-r$ color.  It is difficult to determine
from this illustration if their is any correlation between
$\sigma_a/v_{{\rm H}\alpha}$ and global galaxy color.  One might expect
such a correlation if, for example, galaxies with different global color
have different light-weightings of the thin- vs. thick-disk
\comment{refs; not sure there are relevant ones; Comer\'{o}n?}, which
propagates to a difference in which component dominates the dynamical
pressure in the disk midplane.  Figure \ref{fig:colortrend} assesses
this directly by plotting the error-weighted mean trend in
$\sigma_a/v_{{\rm H}\alpha}$ for quartiles of the $N-r$ distribution of
the AD sample.  The error bars represent the error-weighted standard
deviation of the data in each bin, whereas the error-weighted standard
error is always {\it smaller than the plotted point}.  This suggests a
marginal, yet statistically significant, detection of a slightly larger
$\sigma_a/v_{{\rm H}\alpha}$ in the reddest bin.
